### 2022-11-09 doc/USER_MANUAL/03_mesh_generation.tex
updates headers and usage of geodynamics

\noindent
The basic steps in creating a load-balanced, partitioned mesh with
CUBIT are:
\begin{description}
\item [{1.}] setting up a hexahedral mesh with CUBIT,
\item [{2.}] exporting the CUBIT mesh into a SPECFEM3D Cartesian file format
and
\item [{3.}] partitioning the SPECFEM3D Cartesian mesh files for a chosen
number of cores.
\end{description}
Examples are provided in the SPECFEM3D Cartesian package in the subdirectory
\texttt{EXAMPLES/}. We strongly encourage you to contribute your own
example to this package by contacting the CIG Computational Seismology
Mailing List \urlwithparentheses{cig-seismo@geodynamics.org}.

@@

In each example subdirectory you will find a \texttt{README} file,
which explains in a step-by-step tutorial the workflow for the example.
Please feel free to contribute your own example to this package by
contacting the CIG Computational Seismology Mailing List \urlwithparentheses{cig-seismo@geodynamics.org}.\\

>>>>

\noindent
The basic steps in creating a load-balanced, partitioned mesh with
CUBIT are:
\begin{description}
\item [{1.}] setting up a hexahedral mesh with CUBIT,
\item [{2.}] exporting the CUBIT mesh into a SPECFEM3D Cartesian file format
and
\item [{3.}] partitioning the SPECFEM3D Cartesian mesh files for a chosen
number of cores.
\end{description}
Examples are provided in the SPECFEM3D Cartesian package in the subdirectory
\texttt{EXAMPLES/}. We strongly encourage you to contribute your own
example to this package through the github repository!

@@

In each example subdirectory you will find a \texttt{README} file,
which explains in a step-by-step tutorial the workflow for the example.
Please feel free to contribute your own example to this package through the github repository!

### 2022-11-09 utils/ADJOINT_TOMOGRAPHY_TOOLS/measure_adj/USER_MANUAL/measure_adj_manual.tex
updates headers and usage of geodynamics

To report bugs or suggest improvements to the code, please send an email to the CIG Computational Seismology Mailing List (cig-seismo@geodynamics.org) or Carl Tape (carltape@fas.harvard.edu), and/or use our online bug tracking system Roundup (www.geodynamics.org/roundup).

>>>>

To report bugs or suggest improvements to the code, please use the Issues feature on the github repository.
